### 2024-02-20 documentation/thesis/thesis_document.tex
.

The calculated distances from the \emph{CoG} value of the measurements
to are inserted into a \emph{heapq} priority queue. Subsequently, as
many elements of the queue are returned as defined by the
\emph{IP\_return\_count} parameter. The actual sorting is carried out by
the queue in the background.

@@

\begin{longtable}[]{@{}lll@{}}
\caption{Digital magnetic field sensors characterised for evaluation
\label{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}}\tabularnewline
\toprule
& TLV493D-A1B6 & MMC5603NJ\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D-A1B6 & MMC5603NJ\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D\tabularnewline
Temperature-Sensor & yes & yes\tabularnewline
Resolution {[}uT{]} & 98 & 0.007\tabularnewline
Range {[}mT{]} & ±130.0 & ±3\tabularnewline
Background-Noise {[}uT{]} & 100 & 0.2\tabularnewline
\bottomrule
\end{longtable}

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
are used for sensor characterisation. The selection of sensors is
described in chapter \ref{sensor-selection}. The additional column for
the \emph{Background-Noise} is taken from the respective data sheets of
the sensors and will be verified in the later \emph{Background-Noise}
measurement in chapter \ref{sensor-characterisation-background-noise}.

@@

@@

The sensor platform used is an adapted version of the \emph{1D: Single
Sensor} from chapter \ref{d-single-sensor} sensor platform. The sensors
to be measured are fixed together on an aluminium plate with thermally
conductive adhesive. This compensates for thermal differences. This is
essential for the subsequent temperature deviation tests in order to
obtain comparable measurement results.

@@

\hypertarget{sensor-characterisation-background-noise}{%
\section{Sensor Characterisation:
Background-Noise}\label{sensor-characterisation-background-noise}}

@@

The procedure starts with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{N=10000} measured values is recorded for the baseline
measurement. The output signal of the sensor is continuously measured
and recorded. It is important to carry out the measurement over a
sufficiently lengthy period of time in order to record both short-term
and long-term fluctuations. For this purpose, \emph{N=2000} further
measured values are taken with a trigger and readout rate of one
measurement per second. In order to quantify the noise, the \gls{sd} of
the signal is calculated. These parameters provide information about the
variation of the signal over time and therefore about the sensor
background noise.

@@

The noise of a sensor describes unwanted, random fluctuations or signals
in the measured data. These are clearly recognisable in the figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
in the raw data plot. The baseline determined for each sensor is shown
by the red \(\mu_{rv}\) {[}\(\mu\)T{]} line. It can be seen that each
sensor has a different mean value or baseline offset in the same
environment. For verification, a reference measurement of the
environment is carried out with the calibrated \emph{Voltcraft GM70}
Telsameter next to the sensor \gls{ic}. This provides a reference
baseline value of \emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.

The noise of the sensor is drawn around this using the blue line. For
the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\(^{\mu}\)T},
which is twice the value given by the datasheet as the noise value.
Under the same conditions, the \emph{MMC5603NJ} undercuts the value
specified by the manufacturer. The \gls{sd} approaches
\emph{\(\sigma_{rv}\)=0.20\({\mu}\)T} and is negligible, especially when
additional averaging is used.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensor_evaluation_setup_for_linearity_measurements.png}
\caption{Sensor evaluation setup for linearity measurements
\label{Sensor_evaluation_setup_for_linearity_measurements.png}}
\end{figure}

The sensor linearity of a magnetic field sensor describes the ability of
the sensor to provide a proportional linear response to changes in the
magnetic field without non-linear distortions. This means that the
output signals of the sensor vary directly proportional to the input
magnetic fields without deviations or distortions and is therefore an
important indicator for measurements of fields at different distances or
objects.

This is achieved by means of an additional linear axis installed above
the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
attached to the end effector of this axis, which can thus be moved at
different distances above the respective sensor \gls{ic}. The ambient
temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)C} in the
measurement runs and thus corresponds to the same conditions as in the
\emph{Background-Noise} chapter
\ref{sensor-characterisation-background-noise} setup.

@@

@@

After the sensor baseline has been determined with \emph{N=10000}
samples, the magnet is inserted into the holder. The linear axis is
moved by the user until it is maximally saturated. With the
\emph{TLV493D}, this corresponds to \emph{250.000\(\mu\)T} and below in
low resolution mode. \emph{MCC5603NJ} around \emph{3000\(\mu\)T}. This
ensures that the linearity is determined over the entire measuring
range.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Move the linear axis upwards by the selected distance
\item
  De-energise the axis motor
\item
  Create measurement using \emph{MRPCli} with \emph{N=2000} data points
  per reading
\item
  Export reading to filesystem with current linear axis position in
  meta-data and filename
\end{enumerate}

@@

For both sensors, the deviation is less than \emph{1\%} over the entire
resolution. With the \emph{MMC5603NJ} this is on average only
\emph{0.04\%}. With the \emph{TLV493D} the \gls{sd} is \emph{3.64\%},
for which the deviations at the end in particular (with field strengths
towards zero) are decisive. The previously performed
\emph{Background-Noise} characterisation in chapter
\ref{sensor-characterisation-background-noise} is explained that the
linearity deviation is due to the sensitivity of the sensor.

@@

The temperature sensitivity of magnetic field sensors describes how
sensitively the sensors output is sensitive to temperature changes. It
is important to ensure that temperature fluctuations do not affect
measurement accuracy. A low temperature sensitivity reduces errors due
to temperature changes. An accurate temperature sensitivity
characteristic is therefore crucial for subsequent precise magnetic
field measurements.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
temperature coefficients\tabularnewline
\bottomrule
\end{longtable}

@@

The \emph{TLV493D} performs in noise measurements worse than specified
in the data sheet (\emph{98\(\mu\)T} instead of \emph{175\(\mu\)T}), but
the large measuring range, which fulfils the required specifications
from chapter \emph{Research Question} in chapter
\ref{research-question-and-approach}, must be considered here, which is
not met by the \emph{MMC5603NJ}.

@@

However, due to the limited measuring range of \emph{±3mT}, direct
measurement of stronger magnets is not possible using the
\emph{MMC5603NJ}. The \emph{N45 12x12x12mm} magnets used in the
application typically have a field strength of around \emph{100mT} at a
distance of \emph{10mm} which is more than the \emph{MMC5603NJ} can
measure.

The \emph{TLV493D}, on the other hand, is able to measure these ranges,
but does not achieve the required accuracy due to strong noise and steep
temperature coefficients. In the following chapter, recommendations for
action are defined, which are derived from the analysis results.

>>>>

The calculated distances from the \emph{CoG} value of the measurements
to are inserted into a \emph{heapq} priority queue. As the measured
values are full sphere measurements, the \emph{CoG} in this
implementation is calculated using this formula:

\[\text{CoG} = \frac{\sum{D_{istance} \times W_{eight}}}{\sum{W_{eight}}}\]

Where \emph{\(D_{distance}\)} corresponds to the set distance from the
centre of the magnet to the surface of the sensor \gls{ic}. This is the
same for each measuring point in the measurement and corresponds to the
mechanical structure of the \emph{3D: Full Sphere} \ref{d-full-sphere}
sensor \emph{40mm}. The weighting \emph{\(W_{eight}\)} corresponds here
to the \emph{B}-field value in \(\mu\)T measured by the \emph{TLV493D}
sensor.

Subsequently, as many elements of the queue are returned as defined by
the \emph{IP\_return\_count} parameter. The actual sorting is carried
out by the queue in the background.

@@

\begin{longtable}[]{@{}lll@{}}
\caption{Digital magnetic field sensors characterised for evaluation
\label{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}}\tabularnewline
\toprule
& TLV493D & MMC5603NJ\tabularnewline
\midrule
\endfirsthead
\toprule
& TLV493D & MMC5603NJ\tabularnewline
\midrule
\endhead
Readout-Axis & 3D & 3D\tabularnewline
Temperature-Sensor & yes & yes\tabularnewline
Resolution {[}uT{]} & 98 & 0.007\tabularnewline
Range {[}mT{]} & ±130.0 & ±3\tabularnewline
Background-Noise {[}uT{]} & 100 & 0.2\tabularnewline
\bottomrule
\end{longtable}

The values in table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
were taken from the data sheets of the relevant manufacturers as a
reference for comparison with the later measurement results.

For this evaluation, the sensors listed in the table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}
are used for sensor characterisation. The selection of sensors is
described in chapter \ref{sensor-selection}. The additional column for
the \emph{Background Noise} is taken from the respective data sheets of
the sensors and will be verified in the later \emph{Background Noise}
measurement in chapter \ref{sensor-characterisation-background-noise}.

@@

The following parameters were determined and analysed for the sensor
evaulation:

\begin{itemize}
\tightlist
\item
  Background Noise
\item
  Linearity
\item
  \gls{dr}
\item
  Temperature Sensitivity
\end{itemize}

The characterisation methodology was modified and adapted from
Crescentini,Gibiino and Piero \customcite{CSG22}, as their approaches are
geared towards the analysis of analogue Hall sensors. Direct
transmission is not possible, as their methods are specially tailored to
these sensors. This includes measuring the analogue bias currents and
raw sensor output voltages, which are not accessible with these
digital-only sensors. Adaptations were therefore necessary to extend the
characterisation to the choosen digital sensors
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}.

@@

The sensor platform used is an adapted version of the \emph{1D: Single
Sensor} from chapter \ref{d-single-sensor} sensor platform. The sensors
to be measured are fixed together on an aluminium plate with thermally
conductive adhesive. This compensates for thermal differences. This is
essential for the subsequent temperature deviation tests in order to
obtain comparable measurement results.\customcite{J21}

@@

\hypertarget{sensor-characterisation-backgroundnoise}{%
\section{Sensor Characterisation:
BackgroundNoise}\label{sensor-characterisation-backgroundnoise}}

@@

The procedure starts with the acquisition of the baseline by operating
the sensor without external magnetic fields. For this purpose, a sample
size of \emph{\(N_{baseline}\)=10000} measured values is recorded for
the baseline measurement. The output signal of the sensor is
continuously measured and recorded. It is important to carry out the
measurement over a sufficiently lengthy period of time in order to
record both short-term and long-term fluctuations. For this purpose,
\emph{\(N_{measurement}\)=2000} further measured values are taken with a
trigger and readout rate of one measurement per second. In order to
quantify the noise, the \gls{sd} of the signal is calculated. These
parameters provide information about the variation of the signal over
time and therefore about the sensor background noise.

@@

The noise of a sensor describes unwanted, random fluctuations or signals
in the measured data. These are clearly recognisable in the figure
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}
in the raw data plot. The baseline measurement which was previously
determined for each sensor is shown by the red \(\mu_{rv}\)
{[}\(\mu\)T{]} line. It can be seen that each sensor has a different
baseline offset in the same environment. This variable is the result of
multiple effects, including the electrical offset introduced by the
front end and the effect of the earth's magnetic field \customcite{CSG22}
and the test environment.

For verification, a reference measurement of the environment is carried
out with the calibrated \emph{Voltcraft GM70} Telsameter next to the
sensor \gls{ic}. This provides a reference baseline value of
\emph{\(\mu_{rev}\)=-21.0\(\mu\)T}.

The noise of the sensor is drawn around this using the blue line. For
the \emph{TLV493D} the \gls{sd} \emph{\(\sigma_{rv}\)=172.0\({\mu}\)T},
which is twice the value given by the datasheet as the noise value
(refer to table
\ref{Digital_magnetic_field_sensors_characterised_for_evaluation.csv}).
Under the same conditions, the \emph{MMC5603NJ} undercuts the value
specified by the manufacturer. The \gls{sd} approaches
\emph{\(\sigma_{rv}\)=0.20\({\mu}\)T} and is negligible, especially when
additional averaging is used.

@@

The sensor linearity of a magnetic field sensor or describes the ability
of the sensor to provide a proportional linear response to changes in
the magnetic field without non-linear distortions \customcite{CSG22}. This
means that the output signals of the sensor vary directly proportional
to the input magnetic fields without deviations or distortions and is
therefore an important indicator for measurements of fields at different
distances or objects.

This is achieved by means of an additional linear axis installed above
the sensor setup. A holder for an \emph{N45 12x12x12mm} magnet is
attached to the end effector of this axis, which can thus be moved at
different distances above the respective sensor \gls{ic}. The ambient
temperature is set to \emph{\(\mu_{trev}\)=21.0\(^{\circ}\)C} in the
measurement runs and thus corresponds to the same conditions as in the
\emph{Background Noise} chapter
\ref{sensor-characterisation-background-noise} setup.

@@

In addition, the \gls{dr} for both sensors was measured before the
measurement run to determine the linearity. In this case, this indicates
the minimum and maximum linear measuring range for the selected linear
Hall sensors. A high \gls{dr} enables a more precise detection of
magnetic fields, while a low \gls{dr} can lead to the sensor detecting
magnetic fields outside its detection range \customcite{CSG22}.

@@

After the sensor baseline has been determined with
\emph{\(N_{baseline}\)=10000} samples, the magnet is inserted into the
holder. The linear axis is moved by the user until it is maximally
saturated. With the \emph{TLV493D}, this corresponds to
\emph{250.000\(\mu\)T} and below in low resolution mode.
\emph{MCC5603NJ} around \emph{3000\(\mu\)T}. This ensures that the
linearity is determined over the entire measuring range.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Move the linear axis upwards by the selected distance
\item
  De-energise the axis stepper motor
\item
  Create measurement using \emph{MRPCli} with
  \emph{\(N_{measurement}\)=2000} data points per reading and step
\item
  Export reading to filesystem with current linear axis position in
  meta-data and filename
\end{enumerate}

@@

For both sensors, the deviation is less than \emph{1\%} over the entire
resolution. With the \emph{MMC5603NJ} this is on average only
\emph{0.04\%}. With the \emph{TLV493D} the \gls{sd} is \emph{3.64\%},
for which the deviations at the end in particular (with field strengths
towards zero) are decisive. The previously performed \emph{Background
Noise} characterisation in chapter
\ref{sensor-characterisation-background-noise} is explained that the
linearity deviation is due to the sensitivity of the sensor.

@@

The temperature sensitivity of magnetic field sensors describes how
sensitively the sensors output is sensitive to temperature changes. It
is important to ensure that temperature fluctuations do not affect
measurement accuracy. A low temperature sensitivity reduces errors due
to temperature changes \customcite{J21}. An accurate temperature
sensitivity characteristic is therefore crucial for subsequent precise
magnetic field measurements.

@@

\begin{longtable}[]{@{}lllll@{}}
\caption{Overview of all characterised sensor properties
\label{Overview_of_all_characterised_sensor_properties.csv}}\tabularnewline
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & TLV493D & MMC5603NJ & Unit & Description\tabularnewline
\midrule
\endhead
\(N_{baseline}\) & 10000 & 10000 & - & Number of samples measured for
baseline run\tabularnewline
\(N_{measurement}\) & 2000 & 2000 & - & Number of samples measured for
measurement run\tabularnewline
\(\mu_{nl}\) & 0.79 & 0.00 & \% & Mean noise level\tabularnewline
\(\sigma_{nl}\) & 0.76 & 0.00 & \% & \gls{sd} noise level\tabularnewline
\(\mu_{rv}\) & 157.23 & -50.39 & \(\mu\)T & Mean Baseline without offset
compensation\tabularnewline
\(\sigma_{rv}\) & 172.00 & 0.20 & \(\mu\)T & \gls{sd} sensor
value\tabularnewline
\(\mu_{t}\) & 20.68 & 19.40 & \(^{\circ}\)C & Mean sensor
temperature\tabularnewline
\(\sigma_{t}\) & 0.53 & 0.00 & \(^{\circ}\)C & \gls{sd} sensor
temperature\tabularnewline
\(\mu_{trev}\) & 21.0 & 21.0 & \(^{\circ}\)C & Ambient
temperature\tabularnewline
\(\mu_{sl}\) & 0.25 & 0.04 & \% & Mean sensor linearity
deviation\tabularnewline
\(\sigma_{sl}\) & 3.64 & 0.56 & \% & \gls{sd} sensor
linearity\tabularnewline
\(\mu_{td}\) & -1.99 & -5.13 & \(\mu\)T / \(^{\circ}\)C & Mean sensor
temperature coefficients\tabularnewline
DR & {[}-138;220{]} & {[}-3.1;3.4{]} & \(\mu\)T & maximum linear
\gls{dr}\tabularnewline
\bottomrule
\end{longtable}

@@

The \emph{TLV493D} performs in noise measurements worse than specified
in the data sheet (\emph{98\(\mu\)T} instead of \emph{175\(\mu\)T}), but
the large \gls{dr}, which fulfils the required specifications from
chapter \emph{Research Question} in chapter
\ref{research-question-and-approach}, must be considered here, which is
not met by the \emph{MMC5603NJ}.

@@

However, due to the limited \gls{dr} of around \emph{±3mT}, direct
measurement of stronger magnets is not possible using the
\emph{MMC5603NJ}. The \emph{N45 12x12x12mm} magnets used in the
application typically have a field strength of around \emph{100mT} at a
distance of \emph{10mm} which is more than the \emph{MMC5603NJ} can
measure.

The \emph{TLV493D}, on the other hand, is able to measure these ranges
with a specified \gls{dr} of \emph{±150mT}, but does not achieve the
required accuracy due to strong noise and steep temperature
coefficients. In the following chapter, recommendations for action are
defined, which are derived from the analysis results.
